---
title: "Customer Segmentation Machine Learning"
author: "Author: Lai Yeung"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    number_sections: true
    # highlight: haddock
  # word_document: default
# runtime: shiny
---

<!-- tab.id='tab1', label='tab1', tab.cap="Product Revenue -->
```{css, echo=FALSE}
#header > h1 {
  text-align: center;
  color: Orange;
  font-weight: bold;
}
#header > h4 {
  text-align: right;
  font-weight: bold;
}
h1, #TOC>ul>li {
  font-weight: bold;
}

div.main-container {
  max-width: 2880px;
  margin-left: auto;
  margin-right: auto;
}
```

<!-- .main-container{ -->
<!-- max-width: 1600px !important; -->
<!-- max-width: 100% !important; -->
<!-- max-width: 1600px; -->
<!-- } -->
  
<!-- text front size -->
<style type="text/css">
  body{
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE
                      , message = FALSE
                      , warning = FALSE
                      , dev=c('png')
                      ,ft_show_coltype = FALSE
                      ,ft.align="center"
                      ,tab.topcaption=FALSE
                      ,fig.asp = 0.8, fig.width = 9, out.width = "70%"
                      # ,fig.asp = 0.8, fig.width = 9, out.width = "100%"
                      ,tab.cap.pre="Table")

library(flextable)

set_flextable_defaults(font.size = 11,
  digits = 1, decimal.mark = ".", big.mark = ",",
  na_str = "NA", fmt_date = "%d/%m/%Y")

init_flextable_defaults()

tab_theme <- function(x, ...) {
  x <- x %>% flextable() %>% theme_booktabs(bold_header = TRUE) %>% 
    theme_vanilla() %>% 
    theme_zebra() %>%
    align(align = "center", part = "header") %>% 
    align(align = "right", part = "body")
  autofit(x)
}

use_df_printer()

library(officer)
small_border = fp_border(color="black", width = 1)

# library(shiny)

```

```{r echo = FALSE, include=FALSE}
library(readr) #Fastly write csv
library(readxl) #Fastly write read xlsx
library(writexl)
library(stringr)
library(stringi)
library(dplyr)
library(lubridate)
library(data.table)
library(sqldf)
library(plotly)
library(ggplot2)
library(scales)
library(crosstalk)
library(DT)
library(reshape2)
library(tidyr)
# Sys.setenv(JAVA_HOME='D:/Java/jre1.8.0_202')
# library(xlsx)
library(tcltk)
library(rlang)
library(zoo)
library(summarytools)
library(forcats)

#-------------------------- remove scientific notation
options(scipen=999)
gen_date <- today()
# gen_date <- as.Date("2021-12-31")

setwd("C:/Users/kwanl/Documents/GitHub/Customer_Segmentation_Machine_Learning")
load("Report_Graph.RData")

load("Report_Data.RData")

######################## snapshot time ########################
# Can Adjust depend on snapshot time
data_max_date <- as.Date(as.POSIXct("2022-05-31", tz = "GMT", format = "%Y-%m-%d"))
# data_max_date <- as.Date(max(pos_invoice_prod$TransactionDate))

```

```{r echo = FALSE, include=FALSE}
######################################## ggplot ########################################
theme_ben <- function(base_size = 14) {
  theme_bw(base_size = base_size) %+replace%
    theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1.5), face = "bold", margin = margin(0,0,5,0), hjust = 0.5, color = "gold3"),
      plot.caption = element_text(size = rel(0.8), face = "italic", hjust = 1, color = "grey"),
      # Zone où se situe le graphique
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85), face = "bold"),
      axis.text = element_text(size = rel(0.70), face = "bold"),
      axis.line = element_line(color = "black", arrow = arrow(length = unit(0.3, "lines"), type = "closed")),
      # La légende
      legend.title = element_text(size = rel(0.85), face = "bold"),
      legend.text = element_text(size = rel(0.70), face = "bold"),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      # Les étiquettes dans le cas d'un facetting
      strip.background = element_rect(fill = "#17252D", color = "#17252D"),
      strip.text = element_text(size = rel(0.85), face = "bold", color = "white", margin = margin(5,0,5,0))
    )
}

theme_layout <- function(data, caption = NA_character_, caption_margin = 100, y = -0.18){
  data %>% layout(
    legend = list(title = list(text = "Click below symbol to exclude:")),
    margin = list(b = caption_margin),
    annotations = list(x = 1, y = y, text = paste0("<i>",caption,"</i>"), 
                       showarrow = F, xref='paper', yref='paper', 
                       xanchor='right', yanchor='auto', xshift=0, yshift=0,
                       font=list(size=13, color="#BEBEBE")),
    xaxis = list(autorange = TRUE),
    yaxis = list(autorange = TRUE)
  )
}

title_font <- list(
  size = 14*2,
  color = "rgba(205, 173, 0, 1)")

```

# ) Customer Spending Profile
```{r fig.asp = 0.8, fig.width = 12, out.width = "70%"}
######################################## Cust Spending Amount Quantile ########################################
ggplotly(plot_cust_left_yrs_grp_amt,
         dynamicTicks = TRUE
         # tooltip = c("text")
         ) %>%
  config(displaylogo = FALSE, displayModeBar = TRUE, modeBarButtons = list(list("toImage"), list("zoom2d"), list("select2d"), list("hoverClosestCartesian"), list("hoverCompareCartesian"))) %>% 
  # highlight(on = "plotly_selected", off = "plotly_doubleclick", selected = attrs_selected(showlegend = FALSE)) %>% 
  # theme_layout(caption = "Data source: MNG + WTC", caption_margin = 100) %>%
  layout(
    legend = list(title = list(text = "Click below\nsymbol\n to exclude:")),
    margin = list(t = 150),
    title = list(text = paste0('<b>',"Customer Spending ($)", "By Left Year Group\n", "(Start from ", min(pos_invoice_prod_2$TransactionDate), " to ", data_max_date,")", '</b>'), font = title_font, y = 0.95, x = 0.5),
    # title = list(text = paste0('<b>',"YTD (Jan - ",months(max(raw_data_6$DATE), abbreviate = T),")", '</b>')),
    # xaxis = list(tickformat = ".0%"),
    yaxis = list(tickformat = "$,.0f")
    # title = paste(
    #       '<b>', "Product Revenue($) and Product Qty(#) ", "By Product",'</b>',
    #       '<br><sup><b>', "YTD (Jan - ",months((floor_date(as.Date(gen_date), unit = "month") - 1), abbreviate = T),")",'</b></sup>'
    #     )
  )

# Table Structure: Columns' Name
sketch = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, 'QUANTILE_GRP'),
      th(colspan = 3, '<=2'),
      th(colspan = 3, '2-4'),
      th(colspan = 3, '4-5')
    ),
    tr(
      lapply(rep(c('Quantile', 'Cust #', 'Cust Amt Avg $'), 3), th)
    )
  )
))

temp_data_table <- plot_cust_left_yrs_grp_amt_table

DT::datatable(temp_data_table,
              options = list(paging = TRUE,    ## paginate the output
                             pageLength = 10,  ## number of rows to output for each page
                             scrollX = TRUE,   ## enable scrolling on X axis
                             scrollY = TRUE,   ## enable scrolling on Y axis
                             # autoWidth = TRUE, ## use smart column width handling
                             server = FALSE,   ## use client-side processing
                             dom = 't'
                             # buttons = c('csv', 'excel'),
                             # columnDefs = list(list(targets = '_all', className = 'dt-center'),
                             #                   list(targets = c(0, 8, 9), visible = FALSE))
              ),
              container = sketch,
              # class = 'cell-border stripe',
              selection = list(selectable = FALSE),
              # extensions = 'Buttons',
              # selection = 'single', ## enable selection of a single row
              # filter = 'top',              ## include column filters at the bottom
              rownames = FALSE                ## don't show row numbers/names
) %>% 
  formatCurrency(columns = grep("(Quantile_)|(CUST_AMT_AVG_)", names(temp_data_table), value = T), digits = 0) %>%
  formatRound(columns = grep("(CUST_CNT_)", names(temp_data_table), value = T), digits = 0) %>% 
  formatStyle(
    'Quantile_<=2', 'QUANTILE_GRP',
    backgroundColor = styleEqual(c('quant25', 'quant50', 'quant75'), c('yellow'))
  ) %>% 
  formatStyle(
    c("QUANTILE_GRP_CUST_CNT_2-4", "QUANTILE_GRP_CUST_CNT_4-7"), 'QUANTILE_GRP',
    backgroundColor = styleEqual(c('Total'), c('yellow'))
  ) %>%
  formatStyle(columns = "QUANTILE_GRP",
              target = "row",
              # valueColumns = "PROD_REV_YOY",
              # color = styleInterval(0, c("red", "black")),
              # backgroundColor = styleEqual(c('Total'), c('yellow')),
              backgroundPosition = "center",
              fontWeight = styleEqual(c('Total'), c('bold')),
              `font-size` = "16px")

```

Highlighted in <span style="background-color:yellow">yellow</span>:

Target Spending: Hoping close to Customer Left Year Group <=2

Historical Spending: Use as baseline, ideally not less than before

Approximately:

**_55,984 X Assume Response Rate X \$1,045 + 2,030 X Assume Response Rate X \$599 = Expected Revenue_**

Expected Revenue Details could be using QUANTILE_GRP.

```{r echo = FALSE, include=FALSE}
```

# ) Rencency, Frequency, Monetary Distribution
```{r fig.asp = 0.8, fig.width = 9, out.width = "100%"}
######################################## RFM ########################################
plot_custom_rfm_histograms
```

Rencency: Time since last purchase

Frequency: Store Visit

Monetary: Spending Amount

```{r fig.asp = 1, fig.width = 9, out.width = "70%"}
plot_rfm_bar_chart
#   layout(
#     margin = list(r = 100)
#   )
# plot_rfm_bar_chart$x$layout$annotations[[2]]$text <- "Recency Score"
# plot_rfm_bar_chart$x$layout$annotations[[2]]$x <- 1.08
# plot_rfm_bar_chart$x$layout$annotations[[2]]$textangle <- 90
```

# ) Customer Orders Distribution
```{r}
custom_rfm_order_dist
```
_<span style="color:red">Remarks: Orders actually mean store visit.</span>_

# ) Customer Segment
```{r}
DT::datatable(segment_table_def_final,
              options = list(paging = TRUE,    ## paginate the output
                             pageLength = 10,  ## number of rows to output for each page
                             scrollX = TRUE,   ## enable scrolling on X axis
                             scrollY = TRUE,   ## enable scrolling on Y axis
                             # autoWidth = TRUE, ## use smart column width handling
                             server = FALSE,   ## use client-side processing
                             dom = 't'
                             # buttons = c('csv', 'excel'),
                             # columnDefs = list(list(targets = '_all', className = 'dt-center'),
                             #                   list(targets = c(0, 8, 9), visible = FALSE))
              ),
              # class = 'cell-border stripe',
              selection = list(selectable = TRUE),
              # extensions = 'Buttons',
              # selection = 'single', ## enable selection of a single row
              # filter = 'top',              ## include column filters at the bottom
              rownames = FALSE                ## don't show row numbers/names
)

custom_rfm_bar
```

## Median Recency
```{r fig.asp = 0.8, fig.width = 12, out.width = "70%"}
cust_rfm_plot_median_r
```

## Median Frequency
```{r fig.asp = 0.8, fig.width = 12, out.width = "70%"}
cust_rfm_plot_median_f
```

## Median Monetary
```{r fig.asp = 0.8, fig.width = 12, out.width = "70%"}
cust_rfm_plot_median_m
```

# ) Target Customer Waterfall
```{r}
######################################## RFM ########################################
plot_waterfall_cnt
```

# ) Contact List
```{r}
ggplotly(plot_cust_left_yrs_grp_amt_final_send,
         dynamicTicks = TRUE
         # tooltip = c("text")
) %>%
  config(displaylogo = FALSE, displayModeBar = TRUE, modeBarButtons = list(list("toImage"), list("zoom2d"), list("select2d"), list("hoverClosestCartesian"), list("hoverCompareCartesian"))) %>%
  # highlight(on = "plotly_selected", off = "plotly_doubleclick", selected = attrs_selected(showlegend = FALSE)) %>%
  # theme_layout(caption = "Data source: MNG + WTC", caption_margin = 100) %>%
  layout(
    legend = list(title = list(text = "Click below\nsymbol\n to exclude:")),
    margin = list(t = 150),
    title = list(text = paste0('<b>',"Customer Spending ($)", "By Left Year Group\n", "(Start from ", min(pos_invoice_prod_2$TransactionDate), " to ", data_max_date,")", '</b>'), font = title_font, y = 0.95, x = 0.5),
    # xaxis = list(tickformat = ".0%"),
    yaxis = list(tickformat = "$,.0f")
    # title = paste(
    #       '<b>', "Product Revenue($) and Product Qty(#) ", "By Product",'</b>',
    #       '<br><sup><b>', "YTD (Jan - ",months((floor_date(as.Date(gen_date), unit = "month") - 1), abbreviate = T),")",'</b></sup>'
    #     )
  )

# Table Structure: Columns' Name
sketch = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, 'QUANTILE_GRP'),
      th(colspan = 3, '2-4'),
      th(colspan = 3, '4-5')
    ),
    tr(
      lapply(rep(c('Quantile', 'Cust #', 'Cust Amt Avg $'), 2), th)
    )
  )
))

temp_data_table <- plot_cust_left_yrs_grp_amt_final_send_table

DT::datatable(temp_data_table,
              options = list(paging = TRUE,    ## paginate the output
                             pageLength = 10,  ## number of rows to output for each page
                             scrollX = TRUE,   ## enable scrolling on X axis
                             scrollY = TRUE,   ## enable scrolling on Y axis
                             # autoWidth = TRUE, ## use smart column width handling
                             server = FALSE,   ## use client-side processing
                             dom = 't'
                             # buttons = c('csv', 'excel'),
                             # columnDefs = list(list(targets = '_all', className = 'dt-center'),
                             #                   list(targets = c(0, 8, 9), visible = FALSE))
              ),
              container = sketch,
              # class = 'cell-border stripe',
              selection = list(selectable = FALSE),
              # extensions = 'Buttons',
              # selection = 'single', ## enable selection of a single row
              # filter = 'top',              ## include column filters at the bottom
              rownames = FALSE                ## don't show row numbers/names
) %>%
  formatCurrency(columns = grep("(Quantile_)|(CUST_AMT_AVG_)", names(temp_data_table), value = T), digits = 0) %>%
  formatRound(columns = grep("(CUST_CNT_)", names(temp_data_table), value = T), digits = 0) %>%
  formatStyle(
    'Quantile_<=2', 'QUANTILE_GRP',
    backgroundColor = styleEqual(c('quant25', 'quant50', 'quant75'), c('yellow'))
  ) %>%
  formatStyle(
    c("QUANTILE_GRP_CUST_CNT_2-4", "QUANTILE_GRP_CUST_CNT_4-7"), 'QUANTILE_GRP',
    backgroundColor = styleEqual(c('Total'), c('yellow'))
  ) %>%
  formatStyle(columns = "QUANTILE_GRP",
              target = "row",
              # valueColumns = "PROD_REV_YOY",
              # color = styleInterval(0, c("red", "black")),
              # backgroundColor = styleEqual(c('Total'), c('yellow')),
              backgroundPosition = "center",
              fontWeight = styleEqual(c('Total'), c('bold')),
              `font-size` = "16px")

```

Highlighted in <span style="background-color:yellow">yellow</span>:

Total No. of Customers available to contact.

Historical Spending: Use as baseline, ideally not less than before

Approximately:

Before

**_55,984 X Assume Response Rate X \$1,045 + 2,030 X Assume Response Rate X \$599 = Expected Revenue_**

After

**_46,988 X Assume Response Rate X \$1,018 + 1,684 X Assume Response Rate X \$599 = Expected Revenue_**

Expected Revenue Details could be using QUANTILE_GRP.

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
